Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-12-23 main.tex
Sec. V-A-1-a edited

\section{Experimental evaluation} %: \skug{Full: 3, Polished: 3}}
\label{sec:expe}

We first describe the experimental setup in Section~\ref{sec:setup}. 
Then, we report results on static experiments to assess the performance
of the memory-aware heuristics in Section~\ref{sec.expe.static}, before
discussing the heuristics behavior in a dynamic setting in Section~\ref{sec.expe.dyn}. 
Finally, we report running times of the heuristics in Section~\ref{sec.expe.t}.

\subsection{Experimental setup} %: \skug{Full: 5, Polished: 4}}
    \label{sec:setup}

    All algorithms are implemented in C++ and compiled with g++ (v.8.5.0).
    The experiments are managed by simexpal~\cite{DBLP:journals/algorithms/AngrimanGLMNPT19} and executed on workstations with 192 GB RAM and 2x 12-Core Intel Xeon 6126 @3.2 GHz
    and CentOS 8 as OS.
    Code, input data, and experiment scripts are available to allow reproducibility of results, at~\url{https://zenodo.org/records/13919214}~and~\url{https://zenodo.org/records/13919302}.

    Before presenting the results, we first describe the set of workflows we used for the evaluation, and then the clusters on which the
    workflows were scheduled.
We also explain the way the runtime system works and interacts with our scheduler.

    \subsubsection{Workflow instances}
  %  \skug{Todo: describe the workflows the same asin the abstract}
    We run  experiments on a dataset that consists of real-world workflows: 
    we use workflows coming from~\cite{lotaru} (atacseq, bacass, chipseq,
    eager and methylseq), and also we increase their size using the WFGen generator~\cite{COLEMAN202216}.

@@

    For the size-increased workflows, the graph is produced by the WFGen generator, based on a {\em model workflow} and
    the desired number of tasks.
    We used the real-world workflows as models, except for bacass that lead to errors in the generator.
%
    As number of tasks, we use: 200, \numprint{1000}, \numprint{2000}, \numprint{4000}, \numprint{8000}, \numprint{10000},
    \numprint{15000}, \numprint{18000}, \numprint{20000}, \numprint{25000}, \numprint{30000}.
    We divide the workflows into four groups by size: tiny ones with up to \numprint{200} tasks, small ones with \numprint{1000} to \numprint{8000} tasks,
    middle ones with \numprint{10000} to \numprint{18000} tasks, and big ones with \numprint{20000} to \numprint{30000} tasks.

>>>>

\section{Experimental evaluation}
\label{sec:expe}
%
We first describe the experimental setup in Section~\ref{sec:setup}. 
Then, we report results on static experiments to assess the performance
of the memory-aware heuristics in Section~\ref{sec.expe.static}, before
discussing the heuristics' behavior in a dynamic setting in Section~\ref{sec.expe.dyn}. 
Finally, we report running times of the heuristics in Section~\ref{sec.expe.t}.

\subsection{Experimental setup}
\label{sec:setup}
%
All algorithms are implemented in C++ and compiled with g++ (v.8.5.0).
The experiments are managed by simexpal~\cite{DBLP:journals/algorithms/AngrimanGLMNPT19} and executed on workstations with 192 GB RAM and 2x 12-Core Intel Xeon 6126 @3.2 GHz
and CentOS 8 as OS.
Code, input data, and experiment scripts are available to allow reproducibility of the results at~\url{https://zenodo.org/records/13919214}~and~\url{https://zenodo.org/records/13919302}.

Before presenting the results, we first describe the set of workflows we used for the evaluation and
then the clusters on which the workflows were scheduled.
We also explain the way the runtime system works and interacts with our scheduler.

\subsubsection{Workflow instances}
We run experiments on a set of several real-world workflows from Ref.~\cite{lotaru}
(atacseq, bacass, chipseq, eager, and methylseq). We use the WFGen generator~\cite{COLEMAN202216} to
create larger variants of the workflows above and add the instances created this way to the set.

@@

For the size-increased workflows, the graph is produced by the WFGen generator, based on a {\em model workflow} and
the desired number of tasks.
We used the real-world workflows as models, except for bacass since it leads to errors in the generator.
%
As number of tasks, we use: 200, \numprint{1000}, \numprint{2000}, \numprint{4000}, \numprint{8000}, \numprint{10000},
\numprint{15000}, \numprint{18000}, \numprint{20000}, \numprint{25000}, and \numprint{30000}.
We divide the workflows into four groups by size: tiny ones with up to \numprint{200} tasks, small ones with \numprint{1000} to \numprint{8000} tasks,
middle ones with \numprint{10000} to \numprint{18000} tasks, and big ones with \numprint{20000} to \numprint{30000} tasks.
